Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-06-21 snapshot_system/failover.tex
Added to reliability section to start to tie together the graphs

\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={Node failure affect on VMs},
		xlabel={Failed storage nodes},
		ylabel={VM Availability (\%)},
		%extra y ticks={4.5,5.5,6.5} %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                }
		]
                \addplot[densely dashed,color=blue,mark=square*] table[x=NodesFailed,y=VO2]{figures/vm_failure_2.txt};
                \addplot[densely dashed,color=blue,mark=*] table[x=NodesFailed,y=VO1]{figures/vm_failure_2.txt};
                %\addplot[densely dashed,color=blue,mark=triangle*,mark size=3] table[x=NodesFailed,y=VO3]{figures/vm_failure_2.txt};
                %\addplot[densely dashed,color=blue,mark=diamond*,mark size=3] table[x=NodesFailed,y=VO4]{figures/vm_failure_2.txt};
                \addplot[color=red,mark=square*] table[x=NodesFailed,y=VC2]{figures/vm_failure_2.txt};
                \addplot[color=red,mark=*] table[x=NodesFailed,y=VC1]{figures/vm_failure_2.txt};
                %\addplot[color=red,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/vm_failure_2.txt};
                %\addplot[color=red,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/vm_failure_2.txt};
            \legend{$VO\,10$,$VO\,5$,$VC\,1000$,$VC\,11$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail for VO and VC models for varying average block link counts (i.e. average number of VMs that use a block)}
  \label{fig-vm-availability}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={CDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Availability (\%)},
		%extra y ticks={4.5,5.5,6.5} %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                }
		]
                \addplot[color=blue,mark=*] table[x=NodesFailed,y=VC1]{figures/cds_replication.txt};
                \addplot[color=blue,mark=square*] table[x=NodesFailed,y=VC2]{figures/cds_replication.txt};
                \addplot[color=blue,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/cds_replication.txt};
                \addplot[color=blue,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/cds_replication.txt};
            \legend{$R_C=3$,$R_C=4$,$R_C=5$,$R_C=7$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail in the VC model for different CDS Replication factors (Non-CDS replication fixed at 3, and average CDS block links set to 1000)}
  \label{fig-cds-replication}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%NEW MODEL END%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

To consider the reliability of VM backups in our model, we can consider the likely hood that a data chunk will fail,
given some number of storage node failures. Every time a filesystem chunk fails,
we say that we have lost data for that virtual machine, so it is no longer
available. (in reality it may be only one snapshot that is affected, but it is the user
who must decide which snapshots are important, so we consider the worst case). We use
filesystem chunks rather than data blocks as our unit of failure because the DFS keeps
filesystem chunks as its base unit of storage (in our case there are 16384 blocks in a
filesytem chunk, with 4KB block size and a 64MB chunk size).

We take the likelyhood of VM failure to be the same as the likelyhood of chunk failure,
so
\[
    P_{VMfailure}=\frac{\binom{d}{r}}{\binom{p}{r}}
\]

Since both in the CDS and in the VO approach a single filesystem chunk may be used by many VMs,
we must multiply the block failure ratio by the number of outgoing links for the block to get
the expected impact on the system.
\[
    E_{VMfailure}=L\frac{\binom{d}{r}}{\binom{p}{r}}
\]

in our current testbed we have measured the average number of links
per block (Figure~\ref{vo-links}) and number of links per chunk (Figure~\ref{vo-container-links})
in our dataset. For the complete dataset, we also found the average number of links to CDS chunks, which
was 11 using a 5\% CDS. From Figure~\ref{vo-container-links} you can see that as you add VMs, the average
number of links to a chunk increases. We expect that this trend will level out with larger datasets, but
should continue to increase at a slower rate. For the VC model, we have to consider both CDS chunks and 
Non-CDS chunks. In the VO model all data is shared, but in VC only the CDS data is shared, but at a much
higher rate. This gives a strong advantage to VC, in that for a large percent of the data (95-99\%), there
is only one VM pointing to each Non-CDS chunk. You can see the increase in reliability in Figure~\ref{fig-vm-availability}.
The figure shows that even as the number of links to a CDS chunk increase by 100 times, the availability only decreases
slightly, while in VO even small increases in $L$ causes a large decrease in availability. Figure~\ref{fig-cds-replication}
shows the advantages of increasing the replication factor for CDS blocks. These figures together show
the advantages of the VM-centric model, and the advantages that separating the replication factor for popular blocks
can have on reliability.

\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={Node failure affect on VMs},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                }
		]
                \addplot[densely dashed,color=blue,mark=square*] table[x=NodesFailed,y=VO2]{figures/vm_failure_2.txt};
                \addplot[densely dashed,color=blue,mark=*] table[x=NodesFailed,y=VO1]{figures/vm_failure_2.txt};
                %\addplot[densely dashed,color=blue,mark=triangle*,mark size=3] table[x=NodesFailed,y=VO3]{figures/vm_failure_2.txt};
                %\addplot[densely dashed,color=blue,mark=diamond*,mark size=3] table[x=NodesFailed,y=VO4]{figures/vm_failure_2.txt};
                \addplot[color=red,mark=square*] table[x=NodesFailed,y=VC2]{figures/vm_failure_2.txt};
                \addplot[color=red,mark=*] table[x=NodesFailed,y=VC1]{figures/vm_failure_2.txt};
                %\addplot[color=red,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/vm_failure_2.txt};
                %\addplot[color=red,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/vm_failure_2.txt};
            \legend{$VO\,10$,$VO\,5$,$VC\,1000$,$VC\,11$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail for VO and VC models for varying average block link counts (i.e. average number of VMs that use a block)}
  \label{fig-vm-availability}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={CDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                }
		]
                \addplot[color=blue,mark=*] table[x=NodesFailed,y=VC1]{figures/cds_replication.txt};
                \addplot[color=red,mark=square*] table[x=NodesFailed,y=VC2]{figures/cds_replication.txt};
                \addplot[color=brown,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/cds_replication.txt};
                \addplot[color=black,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/cds_replication.txt};
            \legend{$R_C=3$,$R_C=4$,$R_C=5$,$R_C=7$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail in the VC model for different CDS Replication factors (Non-CDS replication fixed at 3, and average CDS block links set to 1000)}
  \label{fig-cds-replication}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%NEW MODEL END%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
